Case for Support

### 2022-03-03 reviews/responseReviewer_155296694.tex

\documentclass[12pt]{letter}

\usepackage[margin=1.25in]{geometry}

\begin{document}

\begin{letter}{
    BBSRC-BBR Evaluation Committee\\
    Polaris House\\
    North Star Avenue\\
    Swindon, Wiltshire\\
    United Kingdon SN2 1UH
}
\opening{Dear Committee Members,}

We thank the reviewer for his/her comments, that we address below, indexed by
the corresponding sections.

\noindent\textbf{Excellence}

    \texttt{The problem is that building high-level ML objects may hide caveats
    of such algorithms and may make people who use them not understand what
    they are actually doing.}

We share these concerns with the reviewer, that we will address as follows.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods that we will add to Bonsai. We
will provide extensive documentation, and devote ample time in workshops to
explain this functionality.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to build simple and high-quality statistical documentation related to
the interfaced methods.

In addition, for every machine-learning method that we will integrate into
    Bonsai, we will provide recommendations on how to report analysis results.

Critical to help Bonsai users understand the function of the integrated machine
learning methods, and interpret their estimated models' parameters, is to
provide extensive visualisations of these parameters. We will provide such
visualisations.

The Bonsai interfaces that we will develop to machine learning methods will
allow Bonsai users to set any parameter of these methods, and the proposed
documentation will describe in detail the function of all parameters. Although,
we will provide good default values, users will be able to set any parameter
value. In this sense, Bonsai will not be a high-level interface to these
methods.

A central goal of Bonsai is to allow people without programming experience to
perform sophisticated experiments and, with the addition of the proposed
machine-learning functionality, to analyse their results. However, this does
not mean that non-programmers should be ignorant about how the statistical
methods that they are using work. We will help Bonsai users understand the
statistical methods that they use. Programming experience, or deep statistical
knowledge, should not required for this.

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide its users deep understanding of what these methods do.

\noindent\textbf{Uniqueness and Availability}

    \texttt{The added high-level ML tools are already available as free
    packages, but this proposal puts them all together and within the Bonsai
    framework, so the uniqueness is somewhat lower.}

It is true that the machine learning functionality that we propose to
incorporate into Bonsai is already available as free packages. However, people
without much programming experience will most commonly not be able to use this
functionality to control or analyse their experiments. Thus, a first unique
contribution from our proposal is that we will provide machine learning
functionality to people without programming experience, which will most
probably accelerate discovery.

Experimental control and neural data analysis are currently highly
disassociated. Most neuroscientists collect their data and only afterwards
analyse it. This split has had negative consequences for the progress of
neuroscience, as the vast majority of neural data analysis methods are offline
and do not provide key functionality for online experimental control. Hence, a
second unique contribution from our proposal is that it will generate the need
of online data analysis methods, which will generate advances in the field.

\end{letter}

\end{document}

### 2022-03-03 reviews/responseReviewer_155296694.tex

\documentclass[12pt]{letter}

\usepackage[margin=1.25in]{geometry}

\begin{document}

\begin{letter}{
    BBSRC-BBR Evaluation Committee\\
    Polaris House\\
    North Star Avenue\\
    Swindon, Wiltshire\\
    United Kingdom SN2 1UH
}
\opening{Dear Committee Members,}

@@

We thank the reviewer for his/her comments, that we address below, indexed by
the corresponding sections.

\noindent\textbf{Excellence}

\texttt{The problem is that building high-level ML objects may hide caveats of
such algorithms and may make people who use them not understand what they are
actually doing.}

We share these concerns with the reviewer. Some data-analysis open-source
software packages allow users to fit complex statistical models by just
clicking a few buttons in a graphical user interface. And sometimes, this ease
of use leds users to apply these statistical models without sufficient
understanding. We want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods added to Bonsai.  We will provide
extensive written and video documentation explaining these methods.  In
addition, in collaboration with methods authors, we will deliver talks in
workshops explaining the function of added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to build simple and high-quality statistical documentation related to
the interfaced methods.

In addition, for every machine-learning method that we will integrate into
Bonsai, we will provide recommendations on how to report analysis results.
This documentation will be targeted to methods' users, as well as journal and
grant reviewers. It will inform these reviewers what they could expect from
statistical analysis perfromed with methods integrated into the Bonsai
ecosysstem.

@@

Critical to help Bonsai users understand the function of the integrated machine
learning methods, and interpret their estimated models' parameters, is to
provide extensive visualisations of these parameters. We will provide such
visualisations.

The Bonsai interfaces that we will develop to machine learning methods will
allow Bonsai users to set any parameter of these methods, and the proposed
documentation will describe in detail the function of all parameters. Although,
we will provide good default values, users will be able to set any parameter
value. In this sense, Bonsai will not be a high-level interface to these
methods.

A central goal of Bonsai is to allow people without programming experience to
perform sophisticated experiments and, with the addition of the proposed
machine-learning functionality, to analyse their results. However, this does
not mean that non-programmers should be ignorant about how the statistical
methods that they are using work. We will help Bonsai users understand the
statistical methods that they use. Programming experience, or deep statistical
knowledge, should not required for this.

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide users deep understanding of what these methods do.

@@

\noindent\textbf{Uniqueness and Availability}

\texttt{The added high-level ML tools are already available as free packages,
but this proposal puts them all together and within the Bonsai framework, so
the uniqueness is somewhat lower.}

It is true that the machine learning functionality that we propose to
incorporate into Bonsai is already available as free packages. However, people
without much programming experience will most commonly not be able to use this
functionality to control or analyse their experiments. Thus, a first unique
contribution from our proposal is that we will provide machine learning
functionality to people without programming experience, which will most
probably accelerate discovery.

Experimental control and neural data analysis are currently highly
disassociated. Most neuroscientists collect their data and only afterwards
analyse it. This split has had negative consequences for the progress of
neuroscience, as the vast majority of neural data analysis methods are offline
and do not provide key functionality for online experimental control. Hence, a
second unique contribution from our proposal is that it will generate the need
of online data analysis methods, which may generate advances in the field.

### 2022-03-04 reviews/responseReviewer_155296694.tex

We thank the reviewer for his/her comments, that we address below, indexed by
the corresponding sections.

\noindent\textbf{Excellence}

\texttt{The problem is that building high-level ML objects may hide caveats of
such algorithms and may make people who use them not understand what they are
actually doing.}

We share these concerns with the reviewer. Some data-analysis open-source
software packages allow users to fit complex statistical models by just
clicking a few buttons in a graphical user interface. And sometimes, this ease
of use leads users to apply these statistical models without sufficient
understanding. We want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods added to Bonsai. Furthermore, we will provide
extensive written and video documentation explaining the integrated methods. We are currently developing a technical reference  website for Bonsai which is open-source, integrated into the language editor, and open for community contributions. We aim to make extensive use of this website to raise awareness of the details of each method very close to the users.  In
addition, and in collaboration with method authors, we will deliver talks in
workshops explaining the function of added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to building simple and high-quality statistical documentation related to
the interfaced methods.

In addition, for every machine-learning method that we will integrate into
Bonsai, we will provide recommendations on how to report analysis results.
This documentation will be targeted to methods' users, as well as journal and
grant reviewers. It will inform these reviewers what they could expect from
statistical analysis performed with methods integrated into the Bonsai
ecosystem.

Critical to helping Bonsai users understand the function of the integrated machine
learning methods, and interpret their estimated models' parameters, is to
provide extensive visualisations of these parameters. We will provide such
visualisations by taking advantage of Bonsai's built-in data visualisation functionality.

The Bonsai interfaces that we will develop with machine learning methods will
allow Bonsai users to set any parameter of these methods, and the proposed
documentation will describe in detail the function of all parameters. Although,
we will provide good default values, users will be able to set any parameter
value. In this sense, Bonsai will not by itself be a high-level interface to these
methods.

A central goal of Bonsai is to allow people without programming experience to
perform sophisticated experiments and, with the addition of the proposed
machine-learning functionality, to analyse their results. However, this does
not mean that non-programmers should be ignorant about how the statistical
methods that they are using work. We will help Bonsai users understand the
statistical methods that they use. Programming experience, or deep statistical
knowledge, should not be required for this.

@@

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide users deep understanding of what these methods do.

\noindent\textbf{Uniqueness and Availability}

\texttt{The added high-level ML tools are already available as free packages,
but this proposal puts them all together and within the Bonsai framework, so
the uniqueness is somewhat lower.}

It is true that the machine learning functionality that we propose to
incorporate into Bonsai is already available as free packages. However, people
without much programming experience will most commonly not be able to use this
functionality to control or analyse their experiments. Thus, a first unique
contribution from our proposal is that we will provide machine learning
functionality to people without programming experience, which will most
probably accelerate discovery. Bonsai has a good track record of providing advanced functionality to a broad community of users, for example in the existing integration with DeepLabCut (https://elifesciences.org/articles/61909) or the support for dynamic presentation of visual stimuli in BonVision (https://elifesciences.org/articles/65541).

Experimental control and neural data analysis are currently highly
disassociated. Most neuroscientists collect their data and only afterwards
analyse it. This split has had negative consequences for the progress of
neuroscience, as the vast majority of neural data analysis methods are offline
and do not provide key functionality for online experimental control. Hence, a
second unique contribution from our proposal is that it will generate the need
of online data analysis methods, which may generate advances in the field. For example, we have discussed the possibility of enabling and standardising systems for online closed-loop control of behavioural tasks where the results of statistical inference directly feedback to modulate the environment to which animals are exposed. Such novel tasks remain very hard to implement at the moment, and their reproducibility is complicated by the fact that there is no standardised way to easily share such interactive systems. Bonsai is well positioned to address this problem and we expect that the impact of such practices will be very high in the experimentalist community.

### 2022-03-04 reviews/responseReviewer_155296694.tex

\documentclass[12pt]{letter}

\usepackage[hypertexnames=false,colorlinks=true,breaklinks]{hyperref}
\usepackage[margin=1.25in]{geometry}

@@

We thank the reviewer for his/her comments, that we address below, indexed by
the corresponding sections.

\noindent\textbf{Excellence}

\texttt{The problem is that building high-level ML objects may hide caveats of
such algorithms and may make people who use them not understand what they are
actually doing.}

We share these concerns with the reviewer. Some current data-analysis open-source
software packages allow users to fit complex statistical models by just
clicking a few buttons in a graphical user interface. And sometimes, this ease
of use leads users to apply these statistical models without sufficient
understanding. We want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods added to Bonsai. Furthermore, we will provide
extensive written and video documentation explaining the integrated methods. We are currently developing a technical reference  website for Bonsai which is open-source, integrated into the language editor, and open for community contributions. We aim to make extensive use of this website to raise awareness of the details of each method very close to the users.  In
addition, and in collaboration with method authors, we will deliver talks in
workshops explaining the function of added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to building simple and accurate statistical documentation related to
the interfaced methods.

@@

Critical to helping Bonsai users understand the function of the integrated machine
learning methods, and interpret their estimated models' parameters, is to
provide extensive visualisations of these parameters. We will provide such
visualisations by taking advantage of Bonsai's built-in data visualisation functionality.

The Bonsai interfaces that we will develop with machine learning methods will
allow Bonsai users to set any parameter of these methods, and the proposed
documentation will describe in detail the function of all parameters. Although,
we will provide good default values, users will be able to set any parameter
value. In this sense, Bonsai will not by itself be a high-level interface to these
methods.

A central goal of Bonsai is to allow people without programming experience to
perform sophisticated experiments and, with the addition of the proposed
machine-learning functionality, to analyse their results. However, this does
not mean that non-programmers should be ignorant about how the statistical
methods that they are using work. We will help Bonsai users understand the
statistical methods that they use. Programming experience, or deep statistical
knowledge, should not be required for this.

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide users deep understanding of machine learning functionality for
experimental control and neural data analysis.

@@

\noindent\textbf{Uniqueness and Availability}

\texttt{The added high-level ML tools are already available as free packages,
but this proposal puts them all together and within the Bonsai framework, so
the uniqueness is somewhat lower.}

It is not the aim of the proposed resource to develop new machine learning
functionality. We intend to build a resource that can easily integrate into the
experimental control loop existing reliable machine learning functionality
developed by the machine learing community. In this way, the
proposed resource should continuously provide to experimental neuroscientists
up-to-date machine learning functionality. In addition, the resource should
provide methods developers rich datasets on which to assess the performance of
their contributed methods. We believe that these contributions are unique.

Bonsai has a good track record of providing advanced functionality to a broad
community of users, for example in the existing integration with
DeepLabCut\footnote{\url{https://elifesciences.org/articles/61909}} or the
support for dynamic presentation of visual stimuli in
BonVision\footnote{\url{https://elifesciences.org/articles/65541}}. The
proposed machine learning extensions should significantly enhance these
contributions.

Experimental control and neural data analysis are currently highly
disassociated. Most neuroscientists collect their data and only afterwards
analyse it. This split has had negative consequences for the progress of
neuroscience, as the vast majority of neural data analysis methods are offline
and do not provide key functionality for online experimental control. Hence, a
second unique contribution from our proposal is that it will generate the need
of online data analysis methods, which may generate advances in the field. For
example, we have discussed the possibility of enabling and standardising
systems for online closed-loop control of behavioural tasks where the results
of statistical inference directly feedback to modulate the environment to which
animals are exposed. Such novel tasks remain very hard to implement at the
moment, and their reproducibility is complicated by the fact that there is no
standardised way to easily share such interactive systems. Bonsai is well
positioned to address this problem and we expect that the impact of such
practices will be very high in the community of experimental neuroscientists.

### 2022-03-04 reviews/responseReviewers.tex

\documentclass[11pt]{letter}

\usepackage[hypertexnames=false,colorlinks=true,breaklinks]{hyperref}
\usepackage[a4paper, margin=2cm]{geometry}

@@

\begin{document}

\begin{letter}{
}

Thank you for the reviewers' feedback and the opportunity to respond to
comments.

Response to reviewer 175134370:

Regarding the specific comment on reaching new user communities: the proposed
expansion of the Bonsai ecosystem, and the hackathons, workshops etc. mentioned
in the proposal, will be disseminated via numerous methods and fora. Many of
these methods have been successfully used to promote Bonsai thus far, including
professional networks, social media, and engagement with open-source hardware
projects such as Open-Ephys and Neurophotometrics, both of which have actively
promoted Bonsai for use with their systems. As part of the proposed extension,
we will demonstrate Bonsai and its new machine learning functionality at both
experimental and computational neuroscience venues (e.g., BNA's Festival of
Neuroscience, SFN's annual meeting, FENS meetings, Neuromatch Academy,
NeuroIPS, CoSyNe), to engage experimental neuroscience users, as well as new
neural data analysis method developers.

From SWC and GCNU, we will put together a comprehensive communications plan to
engage new communities with Bonsai. We will use a range of communications
channels including owned (SWC and GCNU websites, newsletters), shared (organic
social media) and paid (targeted/boosted social media and paid search)
channels. This could include publishing and publicising longer-form content on
how Bonsai is currently used by the global neuroscience community (e.g. at the
Allen Institute, Janelia Research Campus, etc.) and how the proposed expansion
will enhance this.

We will also empower current users to act as advocates for Bonsai, thereby
maximising reach through existing networks. Group Leaders will promote Bonsai
at conferences during research talks, and we will make targeted approaches to
Group Leaders not currently using the tools who may both benefit from and be
valuable promoters of Bonsai. This will include laboratories both within
neuroscience and from other fields— potentially leveraging user contacts in the
biological and drug screening groups already utilising Bonsai.

\pagebreak

Response to reviewer 155296694:

We share the concerns of the reviewer regarding people using machine learning
methods without understanding them. Some current data-analysis software
packages allow users to fit complex statistical models by just clicking a few
buttons in a graphical user interface. And sometimes, this ease of use leads
users to apply these statistical models without sufficient understanding. We
want to avoid this problem in Bonsai.

@@

The Bonsai interfaces that we will develop with machine learning methods will
allow Bonsai users to set any parameter of these methods, and the proposed
documentation will describe in detail the function of all parameters. Although,
we will provide good default values, users will be able to set any parameter
value. In this sense, Bonsai will not by itself be a high-level interface to these
methods.

A central goal of Bonsai is to allow people without programming experience to
perform sophisticated experiments and, with the addition of the proposed
machine-learning functionality, to analyse their results. However, this does
not mean that non-programmers should be ignorant about how the statistical
methods that they are using work. We will help Bonsai users understand the
statistical methods that they use. Programming experience, or deep statistical
knowledge, should not be required for this.

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide users deep understanding of machine learning functionality for
experimental control and neural data analysis.

Regarding the comment about the lower uniquess of our proposal by the fact that
the machine learning functionality that we proposed to add to Bonsai already
exists as free software package, we would like the make the following
clarifications.

### 2022-03-04 reviews/responseReviewers.tex

\pagebreak

Response to reviewer 155296694:

We share the concerns of the reviewer regarding people using machine learning
methods without understanding them. Some current data-analysis software
packages allow users to fit complex statistical models by just clicking a few
buttons in a graphical user interface. And sometimes, this ease of use leads
users to apply these statistical models without sufficient understanding. We
want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods added to Bonsai. In addition, we
will provide extensive written and video documentation explaining the
integrated methods. We are currently developing a technical reference  website
for Bonsai which is open-source, integrated into the language editor, and open
for community contributions. We aim to make extensive use of this website to
explain relevant aspects of machine learning methods to the Bonsai community.
Furthermore, in collaboration with method authors, we will deliver talks at
workshops explaining the added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to building simple and accurate statistical documentation related to
the interfaced methods.

@@

In addition, for every machine-learning method that we will integrate into
Bonsai, we will provide recommendations on how to report analysis results.
This documentation will be targeted to methods' users, as well as journal and
grant reviewers. It will inform these reviewers what they could expect from
statistical analysis performed with methods integrated into the Bonsai
ecosystem.

Critical to helping Bonsai users understand the function of the integrated
machine learning methods, and interpret their estimated models' parameters, is
to provide extensive visualisations of these parameters. We will provide such
visualisations by taking advantage of Bonsai's built-in data visualisation
functionality.

Our vision is that Bonsai will not only allow its users to run advanced
machine-learning methods, but it will also serve as an educational tool, that
will provide users deep understanding of machinelearning functionality for
experimental control and neural data analysis.

Regarding the comment about the lower uniquess of our proposal by the fact that
the machine learning functionality that we proposed to add to Bonsai already
exists as free software package, we would like to clarify that it is not the
aim of the proposed resource to develop new machine learning functionality. We
intend to build a resource that can easily integrate into the experimental
control loop existing reliable machine learning functionality developed by the
machine learing community. In this way, the proposed resource should provide to
experimental neuroscientists up-to-date machine learning functionality, even
after the finalization of the proposed development, in a sustainable manner. In
addition, the resource should provide methods developers rich datasets on which
to assess the performance of their contributed methods.  We believe that these
contributions are quite unique.

### 2022-03-08 reviews/responseReviewers.tex

Response to reviewer 155296694:

We share the concerns of the reviewer regarding people using machine learning
methods without understanding them. Some current data-analysis software
packages allow users to fit complex statistical models by just clicking a few
buttons in a graphical user interface. And sometimes, this ease of use leads
users to apply these statistical models without sufficient understanding. We
want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the machine learning methods added to Bonsai. In addition, we
will provide extensive written and video documentation explaining the
integrated methods. We are currently developing a technical reference  website
for Bonsai which is open-source, integrated into the language editor, and open
for community contributions. We aim to make extensive use of this website to
explain relevant aspects of machine learning methods to the Bonsai community.
Furthermore, in collaboration with method authors, we will deliver talks at
workshops explaining the added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to building simple and accurate statistical documentation related to
the interfaced methods.

Besides describing clearly in the documentation, and in the graphical user
interface, if suitable, the assumptions of every statistical method, in some
cases we may be able to add automatic tests checking if assumptions of a
statistical method (e.g., gaussianity, or homoscedasticity) are satisfied by the
data on which the method is applied.

@@

In addition, for every machine-learning method that we will integrate into
Bonsai, we will provide recommendations on how to report analysis results.
This documentation will be targeted to methods' users, as well as journal and
grant reviewers. It will inform these reviewers what they could expect from
statistical analysis performed with methods integrated into the Bonsai
ecosystem.

Critical to helping Bonsai users understand the function of the integrated
machine learning methods, and interpret their estimated models' parameters, is
to provide extensive visualisations of these parameters. We will provide such
visualisations by taking advantage of Bonsai's built-in data visualisation
functionality.

Our vision is that Bonsai will not only allow to run advanced machine-learning
methods, but it will also serve as an educational tool, that will provide users
deep understanding of machine learning functionality for experimental control
and neural data analysis.

Regarding the comment about the lower uniqueness of our proposal by the fact that
the machine learning functionality that we proposed to add to Bonsai already
exists as free software package, we would like to clarify that it is not the
aim of the proposed resource to develop new machine learning functionality. We
intend to build a resource that can easily integrate into the experimental
control loop existing reliable machine learning functionality developed by the
machine learning community. In this way, the proposed resource should provide to
experimental neuroscientists up-to-date machine learning functionality, even
after the finalisation of the proposed development, in a sustainable manner. In
addition, the resource should provide methods developers rich datasets on which
to assess the performance of their contributed methods.  We believe that these
contributions are quite unique.

### 2022-03-08 reviews/responseReviewers.tex

\pagebreak

Response to reviewer 155296694:

We share the concerns of the reviewer regarding people using machine learning
methods without understanding them. Some current data-analysis software
packages allow users to fit complex statistical models by just clicking a few
buttons in a graphical user interface. And sometimes, this ease of use leads
users to apply these statistical models without sufficient understanding. We
want to avoid this problem in Bonsai.

We will invest substantial resources to educate Bonsai users about the
functionality of the added machine learning methods. In addition, we will
provide extensive written and video documentation explaining the integrated
methods. We are currently developing a technical reference  website for Bonsai
which is open-source, integrated into the language editor, and open for
community contributions. We aim to make extensive use of this website to
explain relevant aspects of machine learning methods to the Bonsai community.
Furthermore, in collaboration with method authors, we will deliver talks at
workshops explaining the added methods.
%
The Gatsby Computational Neuroscience Unit is a centre of excellence in
statistical neuroscience and machine learning. Its contributions will be
essential to building simple and accurate statistical documentation related to
the interfaced methods.

@@

Besides describing clearly in the documentation, and in the graphical user
interface, if suitable, the assumptions of every statistical method, in some
cases we may be able to add automatic tests checking if assumptions of a
statistical method (e.g., gaussianity, or homoscedasticity) are satisfied by the
data on which the method is applied.

In addition, for every machine-learning method that we will integrate into
Bonsai, we will provide recommendations on how to report analysis results.
This documentation will be targeted to methods' users, as well as journal and
grant reviewers. It will inform these reviewers what they could expect from
statistical analysis performed with methods integrated into the Bonsai
ecosystem.

Critical to helping Bonsai users understand the function of the integrated
machine learning methods, and interpret their estimated models' parameters, is
to provide extensive visualisations of these parameters. We will provide such
visualisations by taking advantage of Bonsai's built-in data visualisation
functionality.

Our aim is that Bonsai will not only allow to run advanced machine-learning
methods, but it will also serve as an educational tool, that will provide users
deep understanding of machine learning functionality for experimental control
and neural data analysis.

One of the largest dangers of allowing users to run complex statistical models
without proper understanding relates to testing statistical significance, which
is a subtle problem, as noted by the reviewer.
%
However, most statistical models we propose to interface with Bonsai will
provide predictive or exploratory functionality, avoiding problems with
significance testing.
%
Some of these models (e.g., latent variable models) may require hypothesis
testing (e.g., comparing which of several models best explains a given
dataset). But most estimations will use Bayesian methods, which are better
suited for hypothesis testing, as noted elsewhere (e.g., Price et al., 2020).

Regarding the comment about the lower uniqueness of our proposal by the fact
that the machine learning functionality that we proposed to add to Bonsai
already exists as free software package, we would like to clarify that it is
not the aim of the proposed resource to develop new machine learning
functionality. We intend to build a resource that can easily integrate into the
experimental control loop existing reliable machine learning functionality
developed by the machine learning community. In this way, the proposed resource
should provide to experimental neuroscientists up-to-date machine learning
functionality, even after the finalisation of the proposed development, in a
sustainable manner. In addition, the resource should provide methods developers
rich datasets on which to assess the performance of their contributed methods.
We believe that both contributions are quite unique.
